Eliminating prior-bias from sparse-projection tomographic reconstructions

### 2020-06-25 paper/tci.tex
rearranged

\subsection{\textbf{Selective prior-based reconstruction}}
\label{sec:selective_prior}

@@

%--------------------------------okra data-------------------------------
\begin{figure}[!h]
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.176\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/okra/testCropped.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
     \caption{Okra 3D dataset: One slice each from the previously scanned objects (the
       first four from the left), and one from the test volume
       (extreme right). In the regions marked in red and green, while
       all slices have deformities, the test
       has none.}
\label{fig:object-prior_test_okra}
\end{figure}
%----------------------------------------------------

@@

\begin{figure}[!h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_1.png}
\captionsetup{labelformat=empty}
        \caption{}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}\\
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_5.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.29\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
      \caption{Sprouts 3D dataset: One slice each from the previously scanned objects (the first five from left) and a slice from the test (extreme
        right).}
\label{fig:object-prior_test_sprouts}
\addtolength{\textfloatsep}{-0.8cm}
\end{figure}
\subsubsection{\textbf{Sprouts dataset}}
\label{Sec:sprouts}
The second dataset consists of six scans of an in vivo
sprout specimen imaged at its various stages of growth
(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated from the given volume of size $130\times130\times130$. In contrast to the scientific
experiment performed for the case of the okra and the potato where we
introduced man-made defects, the changes here are purely the work of
nature. %-----------------------------sprouts 3D results
\begin{figure}[!h]
    \begin{subfigure}[b]{0.29\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
%\captionsetup{labelformat=empty}
        \caption{Test}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
%\captionsetup{labelformat=empty}
        \caption{FDK}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
%\captionsetup{labelformat=empty}
        \caption{l1-ls}
     \end{subfigure}\\
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
%\captionsetup{labelformat=empty}
        \caption{Unselective Prior}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/weightedPriorIm.png}
%\captionsetup{labelformat=empty}
        \caption{Selective prior}
     \end{subfigure}
     \caption{3D reconstruction of sprouts from $2.5\%$ projection views
   (b, c) have poor details (d) no new information detected (the
   prior dominates as can be seen in the blue and red regions) and
   (e) new information detected in the regions of interest. The reconstructed volumes can be viewed in ~\cite{supp_paper}.} 
\label{fig:sprouts_3D_results}
%\addtolength{\textfloatsep}{-0.8cm}
\end{figure}

>>>>

 \section{Resuls: Reconstruction by unselective prior}
 %--------------------------------okra data-------------------------------
\begin{figure}[!h]
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_1.png}
\captionsetup{labelformat=empty}       
 \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.18\linewidth}
        \includegraphics[width=\textwidth]{../images/okra/templateCropped_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.176\linewidth}
        \fcolorbox{yellow}{yellow}{\includegraphics[width=\textwidth]{../images/okra/test.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
     \caption{Okra 3D dataset: One slice each from the previously scanned objects (the
       first four from the left), and one from the test volume
       (extreme right). In the regions marked in red and green, while
       all slices have deformities, the test
       has none.}
\label{fig:object-prior_test_okra}
\end{figure}
%----------------------------------------------------

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.185\columnwidth]{../images/okra/test.png}}}\hfill
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/fdk_cropped.png}}\hfill
\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/okra/cs_cropped.png}}\hfill
\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\caption{3D reconstruction of the okra from $10\%$ projection
  views (b) has strong streak artefacts, (c) blurred, (d) The prior enables better reconstruction.The reconstructed volumes can be viewed in ~\cite{supp_paper}.}
\label{fig:okra_3D_results_unselective}
\end{figure}

%---------------------------------------
\begin{table}[!h]
  \centering
  \caption{SSIM of the full reconstructed okra volume by various methods.}
\begin{tabular}{|l|c|c|c|c|}
\hline
                   &  \textbf{\begin{tabular}[c]{@{}c@{}}Ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} \\ \hline
\textbf{full Volume} & 1 (ideal)                     & 0.87        &  0.92       & \textcolor{red}{0.95}                                                                                   \\ \hline
\end{tabular}
\label{table:okra_ssim_full_volume}
\end{table}

\begin{figure}[!h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_1.png}
\captionsetup{labelformat=empty}
        \caption{}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_2.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_3.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}\\
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_4.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/template_5.png}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.29\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
\captionsetup{labelformat=empty}
        \caption{}
     \end{subfigure}
      \caption{Sprouts 3D dataset: One slice each from the previously scanned objects (the first five from left) and a slice from the test (extreme
        right).}
\label{fig:object-prior_test_sprouts}
\addtolength{\textfloatsep}{-0.8cm}
\end{figure}
 %-----------------------------sprouts 3D results
\begin{figure}[!h]
    \begin{subfigure}[b]{0.29\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
%\captionsetup{labelformat=empty}
        \caption{Test}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
%\captionsetup{labelformat=empty}
        \caption{FDK}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
%\captionsetup{labelformat=empty}
        \caption{l1-ls}
     \end{subfigure}\\
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
%\captionsetup{labelformat=empty}
        \caption{Unselective Prior}
     \end{subfigure}
     \caption{3D reconstruction of sprouts from $2.5\%$ projection views
   (b, c) have poor details (d) no new information detected (the
   prior dominates as can be seen in the blue and red regions) and
   (e) new information detected in the regions of interest. The reconstructed volumes can be viewed in ~\cite{supp_paper}.} 
\label{fig:sprouts_3D_results}
%\addtolength{\textfloatsep}{-0.8cm}
\end{figure}

\begin{table}
  \centering
  \caption{SSIM of the full reconstructed sprouts volume by various methods.}
\begin{tabular}{|l|c|c|c|c|}
\hline
                   & \textbf{\begin{tabular}[c]{@{}c@{}}ground\\truth\end{tabular}} & \textbf{FDK} & \textbf{l1-ls} & \textbf{\begin{tabular}[c]{@{}c@{}}Unselective\\prior + l1-ls\end{tabular}} \\ \hline
\textbf{Full volume}   & 1 (ideal)                    & 0.82        & 0.71       & \textcolor{red}{0.92}                                                                                                                       \\ \hline
\end{tabular}
\label{table:sprouts_ssim}
\end{table}
%----------------------------------------------------------------------
\section{Method:Selective prior-based reconstruction}
\label{sec:selective_prior}

@@

%----------------------------------------------------

@@

\subsubsection{\textbf{Sprouts dataset}}
\label{Sec:sprouts}
The second dataset consists of six scans of an in vivo
sprout specimen imaged at its various stages of growth
(Fig.~\ref{fig:object-prior_test_sprouts}). Projections were generated from the given volume of size $130\times130\times130$. In contrast to the scientific
experiment performed for the case of the okra and the potato where we
introduced man-made defects, the changes here are purely the work of
nature. %-----------------------------sprouts 3D results
\begin{figure}[!h]
    \begin{subfigure}[b]{0.29\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
%\captionsetup{labelformat=empty}
        \caption{Test}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
%\captionsetup{labelformat=empty}
        \caption{FDK}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
%\captionsetup{labelformat=empty}
        \caption{l1-ls}
     \end{subfigure}\\
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
%\captionsetup{labelformat=empty}
        \caption{Unselective Prior}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/weightedPriorIm.png}
%\captionsetup{labelformat=empty}
        \caption{Selective prior}
     \end{subfigure}
     \caption{3D reconstruction of sprouts from $2.5\%$ projection views
   (b, c) have poor details (d) no new information detected (the
   prior dominates as can be seen in the blue and red regions) and
   (e) new information detected in the regions of interest. The reconstructed volumes can be viewed in ~\cite{supp_paper}.} 
\label{fig:sprouts_3D_results}
%\addtolength{\textfloatsep}{-0.8cm}
\end{figure}
